Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-11 ms/response_letter.Rmd

> 2. A crucial thing for readers to know is how to "convert" one method's estimate of LMA to another: the authors could report an equation (or a few, accounting for some additional covariates such as leaf area and leaf thickness, which this paper identifies as important modifiers of the relationship) that scholars could use in the future if trying to compare LMA estimates collected using different methods. In other words, taking the eq from Appendix 2 and modifying it given the results of this study.

Thank you.
This is an important thing to clarify.
We now use a linear model that used leaf area and leaf thickness as covariates but we suggest OLS models without covariates for the conversion of LMA because leaf thickness and leaf area affect not only the mean but also the variance in the relationship between the leaf disc and whole-leaf estimates, and that is why R2 values changed among the four groups (thin vs. think and small vs. large leaves) and it is not to practical to convert LMA using leaf area or leaf thickness.
We also present a practical guideline for conversion of LMA.

> 3. I am confused and unconvinced by the inclusion and discussion of intraspecific trait variation on several levels. First, the authors do not clearly explain ITV, its importance, or its relevance to LMA. Secondly, the methods used to quantify ITV are not recommended (see Yang et al 2020. Large underestimation of intraspecific trait variation and its improvements. Frontiers in Plant Science); ideally the authors should use Bao's CV estimator. Finally, there is little interpretation of the results of their analysis. I think this metric needs to either be excluded entirely or significantly expanded upon.

Thank you.
We have cited the recent review by Westerband et al. as well as other works to explain ITV, its importance and the extent of ITV for LMA.
We now use Bao's CV estimator (CV4) instead of the coefficient of variation of log-normally distributed data ($CV = \sqrt{exp(s_{\mathrm{ln}}^2) - 1}$).
We also limited to the analysis for species that have at least 5 individuals.
The relationship between the two estimates became much weaker (Fig. 4).

@@

> L69-73 This sentence is crucial for your hypotheses but is buried in the middle of this paragraph. I suggest breaking this paragraph (beginning on line 63) up into 2: the first describing different methods of measurement and how commonly each are used, and any previous attempts to compare them. The second paragraph can get into which leaf types are likely to give similar or different estimates based on the two metrics and why.

Thank you.
We now break up the paragraph into two sections: the first describing the different methods and their record numbers in TRY, and previous works that compared them, and the second describing the expected effects of leaf morphology on the relationship between whole-leaf and leaf disc LMA.

> L82-84 I find this introduction of ITV to be confusing. ITV has a robust literature which is not cited here (for a recent review, see Westerband, Funk, and Barton, 2021. Intraspecific trait variation in plants: a renewed focus on its role in ecological processes. Annals of botany). The authors should briefly introduce this concept and it's ecological relevance before applying it to their question of which method generates greater estimates of ITV and why.

Thank you.
As noted above, We have cited the recent review by Westerband et al. as well as other works to explain ITV, its importance and the extent of ITV for LMA.

@@

> L154-160 see major comment 3

Thank you.
We now use Bao's CV as noted above.

> L169-172 This is the major result of the paper. I suggest making it the first line of the results section (however I would modify it to fit the individual, rather than species-mean, level data: see below).

Thank you.
We have started the result section with the shift in elevation between whole-leaf and leaf disc LMA (i.e., whole-leaf LMA is greater than leaf disc LMA) .
Please see our response for using species- vs. individual-level data below.

@@

> L175-176 Based on this, I am confused about the statistical approach. Did the authors separately run regressions for species-level means and individual level means? If so, it is almost a statistical inevitability that the individual level analysis would have a lower r2 than the species level analysis: therefore I would not report this as a result, per se. In addition, the species level means is more or less meaningless in the context of this paper: much more importantly is the comparison of individual based measurements. I would therefore remove the species level results form the manuscript, and instead only report on the individual level data.

Thank you.
We agree that using both species- and individual-level data in the same statistical framework is confusing and not appropriate.
Instead of using individual-level data, we now only use the species-level data
For individual-level data, variance among species are not independent, and thus SMA or OLS regressions are not appropriate.
Analyses of individual-level data requires mixed linear models with species-level errors, but this is not useful for the context of our paper.
We therefore only report species-level results.

@@

> L182 I believe leaf punch size was something that varied between datasets, and was never measured on the same leaves. I'm therefore confused as to how the authors are interpreting the effect of "leaf punch size" in their models: could this not simply be a reflection of the different species represented in the different datasets?

Thank you.
We now include other continuous variables (leaf tissue density, leaf area, and leaf thickness) as covariates in our model, and thus we have some confidence in the effect of leaf punch.
However, as the reviewer pointed out, we should have used the same leaf punch size or repeated measurements using different leaf punch sizes.
We consider this as a limitation of our study and explain this in the discussion.

@@

> L183-184 Which metric had higher ITV? That is a more relevant result than simply the R2 value.

Leaf disc LMA had higher ITV.
We have added the paired t-test for this in the results section.

@@

> In the Introduction section, the authors had better add some introduction to the leaf disc sampling method, since this method was focused to make a comparison with the whole-leaf sampling method for calculating LMA.

???

> The authors had better explain why they used the LMA values with leaf petioles mass.

Thank you.
We have added the records of TRY database that shows LMA including petioles are very common.

@@

> Line 1: Suggest adding "- evidence from 334 woody species" in the title.

Thank you.
We keep the original title as recommended by the editor.

> Lines 26 and 51: Change "the key trait" to "an important functional trait".

Thank you.
We have updated the first one but keep the second one as "a key trait" because we have added the explanation on why LMA is considered as "a key trait" in the LES at the beginning of the introduction.

@@

> Line 57: I think that the following reference helps to support this statement, because LMA values were found to vary across leaf age, and LMA also exhibits a plasticity to climate when leaves enter the maturation stage (Jiao et al., 2022).
> Jiao, Y., Niklas, K.J., Wang, L., Yu, K., Li, Y., Shi, P. 2022. Influence of leaf age on the scaling relationships of lamina biomass vs. area. Frontiers in Plant Science In press.

Thank you.
** this should be somewhere else and not line 57**.
We have cited it in XX.

@@

> Li, Y., Zheng, Y., Ratkowsky, D.A., Wei, H., Shi, P. 2022. Application of an ovate leaf shape model to evaluate leaf bilateral asymmetry and calculate lamina centroid location. Frontiers in Plant Science, 12: 822907. doi: 10.3389/fpls.2021.822907

Thank you.
We have cited these now.

> Lines 97 and 98: Drop the numerical values of R squared. There is no need to exhibit the results here.

Thank you, but to make the statement of "good correlations" more quantitative, we do feel showing *R^2^* values is still useful.
We, therefore, kept the *R^2^* values in the introduction.

@@

> Lines 105 and 106: Why did you only collect the data in China and Japan. Here, I think, you had better add one to three sentences to explain the feasibility of showing general results for other floras.

Thank you.
We have added MAT and MAP in the main text to support that our dataset covers the wide climate ranges in the distribution of broad-leaved tree species.

> Lines 124 and 125: Why did you maintain leaf petiole in calculating LMA? It is strange for me, because it might inflate LMA given that its definition is dry mass per unit leaf area. What is the meaning for "avoiding thick veins"? Do you mean in the experiment you punch the positions without having the secondary order veins?

Thank you.
The main function of leaves is to deliver a profitable return on the investment that has been made in constructing the leaf (Westoby, Reich and Wright 2013), and thus it is also natural to include leaf petiole in LMA.
As noted above, we have added the records of TRY database that shows LMA including petioles are actually very common.

We now more clearly explain that thick veins are secondary order veins.

@@

> Lines 129-131: Can you class the leaf shapes of 334 woody species you have used? It will affect your sampling positions you are describing here.

Thank you.
It is hard to classify the leaf shapes of each species.
Instead, we have added the detailed LMA measurement protocol including sampling positions for different types of leaf shapes in Appendix S2.

@@

> Lines 151-153: I think, a frequency of LA is needed as a supplementary figure to show the feasibility of such division.

Thank you.
As noted above, we have removed the analysis grouping species into the different categories.

@@

> Line 163: It is incorrect to use 1000 bootstrap replates to calculate a confidence interval! In general, >= 30 replates are enough for calculating a standard deviation, and >= 2000 replates to calculate a confidence interval.

Thank you.
We now use 2000 replicates.

> Lines 168 and 169: It is a strange result for me. Leaf area has been demonstrated to be negatively correlated to mean leaf thickness at the species level (see Figure 4 in Lin et al., 2018). It seems that you obtained a negative correlation based on the pooled data of biomes. If possible, I suggest adding several sentences to discuss the reasons for the pooled data in the Discussion section.

Thank you.
We originally had this result to support grouping species into four categories, because if the correlation between leaf area and leaf thickness are too strong, we cannot group species into four categories based on median values of traits.
As noted above, we removed the analysis of grouping species, and thus we also removed this result.

### 2022-05-11 ms/LMA_method.Rmd
update ms

The primary function of leaves is to return photosynthetic revenue on the investment that has been made in constructing the leaf [i.e., leaf economic spectrum, @Wright2004a; @Westoby2013].
Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is the key trait of the leaf economic spectrum [@Wright2004a; @Poorter2009; @Onoda2017].
Generally, resource-acquisitive species (fast-growing species) tend to have low LMA values, showing high photosynthesis, high nutrients, and often have fast leaf turnover [@Wright2004a].
In contrast, resource-conservative species (slow-growing species) often have higher LMA values with the opposite patterns [@Garnier1994; @Wright2004a; @Reich2014; @Diaz2016].
The LMA is also frequently used in plant growth analysis [@Evans1972; @Poorter2014; @Falster2018] because relative growth rates (RGR) can be decomposed into the product of net assimilation rate (NAR), leaf mass ratio (LMR) and LMA (i.e., RGR = NAR $\times$  LMR $\times$ LMA^-1^).
Another appealing feature of LMA is that it is relatively easy to measure large numbers of species [i.e., 'soft' trait, @Diaz2004].
Therefore, LMA has been of interests to ecologists and widely used since the first report more than a century ago [@Hanson1917].
Actually, LMA has one of the best species coverage in leaf traits of the TRY plant data database (16,460 species) and was also the most often requested leaf trait (2,977 out of 7,330 requests), followed by leaf by leaf nitrogen (N) contents per leaf dry mass [12,238 species, 1,938 requests, @Kattge2020 [TRY version 5, status October 1 2019]]

@@

Since larger leaves tend to invest more of their mass into dense midribs and petiole for support [@Niinemets2006; @Niinemets2007], and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; [@Grubb1986]), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.
(**add leaf density**)
If leaf disc LMA largely and consistently underestimates whole-leaf LMA (i.e., differences in means), some calibrations may be required to combine or compare those different estimates [@Kraft2008; @Onoda2011].
If divergencies between the estimates based on the different methods are large and inconsistent (i.e., differences in variances and low *R^2^* values), this is difficult to calibrate and should inflate errors in the subsequent analyses.
To date, however, only a database from a single region, Panama Plant Traits Database [@Wright2010], is available in the TRY [@Kattge2020] that have both estimates of LMA from small leaf discs and whole leaves including petioles, limiting of our understanding of under what conditions estimates of LMA from leaf discs are reliable estimates of whole-leaf LMA.

@@

A bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were summarized with variance explained (*R^2^*) based on Pearson correlations and with standardized major axis (SMA) regressions [@Warton2006] across all the species.

SMA analyses were run using the R package *smatr* [@Warton2012a]; this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
Confidence intervals of SMA estimates were based on 2000 bootstraps.

@@

where $\tilde{\sigma_i}$ is a hyperparameter for $\sigma_i$ ,
$\omega^2$ is a scaling hyperparameter, and $\gamma$ are coefficients.
To allow comparisons among parameter estimates, $\mathrm{ln}(LD)$, $\mathrm{ln}(LA)$, and $\mathrm{ln}(LT)$ were scaled to a mean of 0 and standard deviation of 1.
Note that this model does not include measurement errors of leaf disc LMA implemented in the following analysis, because there are too many scaling parameters

Posterior distributions of all parameters were estimated using the Hamiltonian Monte Carlo algorithm (HMC) implemented in Stan [@Carpenter2017] using the weakly-informative priors [@Gelman2008].
See supplement XXXX for more detail.
The Stan code use to fit models is available from Github at: [https://github.com/mattocci27/leaf-disc](https://github.com/mattocci27/leaf-disc).
Convergence of the posterior distribution was assessed with the Gelman-Rubin statistic with a convergence threshold of 1.1 for all parameters [@Gelman2013].

@@

where $CV_1 = s/\bar{x}$, $s$ is the sample standard deviation and $\bar{x}$ is the sample mean, *N* is the sample size, and $\gamma_1$ and $\gamma_2$ are the skewness and kurtosis of the trait distribution.
Bao's CV estimator is a robust method to quantify ITV based on coefficient of variation (CV) when sample size is small [@Yang2020].
We calulcated CV for species that have at least 5 indivdiuals as recommended in @Westerband2021.
Ideally, 20 individuals for each species are required for robust estimation of CV [i.e., <5% differences from the true ITV; @Yang2020].

@@

**Fig. 4.**
Relationships between coefficient of variation (Bao's CV estimator, Eq. 5) in leaf trait values determined by using whole leaves and leaf discs: (a) leaf mass per area (LMA).
The correlation is significant (*P* < 0.001).
Details as in Fig. 1.

>>>>

The primary function of leaves is to return photosynthetic revenue on the investment that has been made in constructing the leaf [i.e., leaf economic spectrum, @Wright2004a; @Westoby2013].
Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is a key trait in the leaf economic spectrum [@Wright2004a; @Poorter2009; @Onoda2017].
Generally, resource-acquisitive species (fast-growing species) tend to have low LMA values, showing high photosynthesis, high nutrients, and often have fast leaf turnover [@Wright2004a].
In contrast, resource-conservative species (slow-growing species) often have higher LMA values with the opposite patterns [@Garnier1994; @Wright2004a; @Reich2014; @Diaz2016].
The LMA is also frequently used in plant growth analysis [@Evans1972; @Poorter2014; @Falster2018] because relative growth rates (RGR) can be decomposed into the product of net assimilation rate (NAR), leaf mass ratio (LMR) and LMA (i.e., RGR = NAR $\times$  LMR $\times$ LMA^-1^).
Another appealing feature of LMA is that it is relatively easy to measure large numbers of species [i.e., 'soft' trait, @Diaz2004].
Therefore, LMA has been of interests to ecologists and widely used since the first report more than a century ago [@Hanson1917].
Actually, LMA has one of the best species coverage in leaf traits of the TRY plant data database (16,460 species) and was also the most often requested leaf trait (2,977 out of 7,330 requests), followed by leaf by leaf nitrogen (N) contents per leaf dry mass [12,238 species, 1,938 requests, @Kattge2020 [TRY version 5, status October 1 2019]]

@@

Since larger leaves tend to invest more of their mass into dense midribs and petiole for support [@Niinemets2006; @Niinemets2007; @Li2022; @Li2022a], and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; [@Grubb1986]), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.
(**add leaf density**)
If leaf disc LMA largely and consistently underestimates whole-leaf LMA (i.e., differences in means), some calibrations may be required to combine or compare those different estimates [@Kraft2008; @Onoda2011].
If divergencies between the estimates based on the different methods are large and inconsistent (i.e., differences in variances and low *R^2^* values), this is difficult to calibrate and should inflate errors in the subsequent analyses.
To date, however, only a database from a single region, Panama Plant Traits Database [@Wright2010], is available in the TRY [@Kattge2020] that have both estimates of LMA from small leaf discs and whole leaves including petioles, limiting of our understanding of under what conditions estimates of LMA from leaf discs are reliable estimates of whole-leaf LMA.

@@

A bivariate trait relationship between disc-based and whole-leaf log-transformed LMA was summarized with variance explained (*R^2^*) based on Pearson correlations and with a standardized major axis (SMA) regression [@Warton2006] across all the species.

A SMA analysis was run using the R package *smatr* [@Warton2012a]; this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
Confidence intervals of SMA estimates were based on 2000 bootstraps.

@@

where $\tilde{\sigma_i}$ is a hyperparameter for $\sigma_i$ ,
$\omega^2$ is a scaling hyperparameter, and $\gamma$ are coefficients.
To allow comparisons among parameter estimates, $\mathrm{ln}(LD)$, $\mathrm{ln}(LA)$, and $\mathrm{ln}(LT)$ were scaled to a mean of 0 and standard deviation of 1.
Note that this model does not include measurement errors of leaf disc LMA implemented in the previous SMA analysis, because there are too many scaling parameters

Posterior distributions of all parameters were estimated using the Hamiltonian Monte Carlo algorithm (HMC) implemented in Stan [@Carpenter2017] using the weakly-informative priors [@Gelman2008].
See Appendix SX for more detail.
The Stan code use to fit models is available from Github at: [https://github.com/mattocci27/leaf-disc](https://github.com/mattocci27/leaf-disc).
Convergence of the posterior distribution was assessed with the Gelman-Rubin statistic with a convergence threshold of 1.1 for all parameters [@Gelman2013].

@@

where $CV_1 = s/\bar{x}$, $s$ is the sample standard deviation and $\bar{x}$ is the sample mean, *N* is the sample size, and $\gamma_1$ and $\gamma_2$ are the skewness and kurtosis of the trait distribution.
Bao's CV estimator is a robust method to quantify ITV based on a coefficient of variation (CV) when sample size is small [@Yang2020].
We calulcated CV for species that have at least 5 indivdiuals as recommended in @Westerband2021.
Ideally, 20 individuals for each species are required for robust estimation of CV [i.e., <5% differences from the true ITV; @Yang2020].

@@

**Fig. 4.**
Relationships between coefficient of variation (Bao's CV estimator, Eq. 5) in LMA values determined by using whole leaves and leaf discs.
The correlation is significant (*P* < 0.001).
Details as in Fig. 1.

### 2022-05-11 ms/LMA_method.tex
update ms

The primary function of leaves is to return photosynthetic revenue on the investment that has been made in constructing the leaf (i.e., leaf economic spectrum, \protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Westoby2013}{Westoby et al., 2013}).
Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is the key trait of the leaf economic spectrum (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Poorter2009}{Poorter et al., 2009}; \protect\hyperlink{ref-Onoda2017}{Onoda et al., 2017}).
Generally, resource-acquisitive species (fast-growing species) tend to have low LMA values, showing high photosynthesis, high nutrients, and often have fast leaf turnover (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}).
In contrast, resource-conservative species (slow-growing species) often have higher LMA values with the opposite patterns (\protect\hyperlink{ref-Garnier1994}{Garnier and Laurent, 1994}; \protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Reich2014}{Reich, 2014}; \protect\hyperlink{ref-Diaz2016}{Díaz et al., 2016}).
The LMA is also frequently used in plant growth analysis (\protect\hyperlink{ref-Evans1972}{Evans, 1972}; \protect\hyperlink{ref-Poorter2014}{Poorter et al., 2014}; \protect\hyperlink{ref-Falster2018}{Falster et al., 2018}) because relative growth rates (RGR) can be decomposed into the product of net assimilation rate (NAR), leaf mass ratio (LMR) and LMA (i.e., RGR = NAR \(\times\) LMR \(\times\) LMA\textsuperscript{-1}).
Another appealing feature of LMA is that it is relatively easy to measure large numbers of species (i.e., `soft' trait, \protect\hyperlink{ref-Diaz2004}{Díaz et al., 2004}).
Therefore, LMA has been of interests to ecologists and widely used since the first report more than a century ago (\protect\hyperlink{ref-Hanson1917}{Hanson, 1917}).
Actually, LMA has one of the best species coverage in leaf traits of the TRY plant data database (16,460 species) and was also the most often requested leaf trait (2,977 out of 7,330 requests), followed by leaf by leaf nitrogen (N) contents per leaf dry mass (12,238 species, 1,938 requests, \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020} {[}TRY version 5, status October 1 2019{]})

@@

Since larger leaves tend to invest more of their mass into dense midribs and petiole for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006}, \protect\hyperlink{ref-Niinemets2007}{2007}), and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986})), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.
(\textbf{add leaf density})
If leaf disc LMA largely and consistently underestimates whole-leaf LMA (i.e., differences in means), some calibrations may be required to combine or compare those different estimates (\protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}).
If divergencies between the estimates based on the different methods are large and inconsistent (i.e., differences in variances and low \emph{R\textsuperscript{2}} values), this is difficult to calibrate and should inflate errors in the subsequent analyses.
To date, however, only a database from a single region, Panama Plant Traits Database (\protect\hyperlink{ref-Wright2010}{Wright et al., 2010}), is available in the TRY (\protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020}) that have both estimates of LMA from small leaf discs and whole leaves including petioles, limiting of our understanding of under what conditions estimates of LMA from leaf discs are reliable estimates of whole-leaf LMA.

@@

A bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were summarized with variance explained (\emph{R\textsuperscript{2}}) based on Pearson correlations and with standardized major axis (SMA) regressions (\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the species.

SMA analyses were run using the R package \emph{smatr} (\protect\hyperlink{ref-Warton2012a}{Warton et al., 2012}); this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
Confidence intervals of SMA estimates were based on 2000 bootstraps.

@@

where \(\tilde{\sigma_i}\) is a hyperparameter for \(\sigma_i\) ,
\(\omega^2\) is a scaling hyperparameter, and \(\gamma\) are coefficients.
To allow comparisons among parameter estimates, \(\mathrm{ln}(LD)\), \(\mathrm{ln}(LA)\), and \(\mathrm{ln}(LT)\) were scaled to a mean of 0 and standard deviation of 1.
Note that this model does not include measurement errors of leaf disc LMA implemented in the following analysis, because there are too many scaling parameters

Posterior distributions of all parameters were estimated using the Hamiltonian Monte Carlo algorithm (HMC) implemented in Stan (\protect\hyperlink{ref-Carpenter2017}{Carpenter et al., 2017}) using the weakly-informative priors (\protect\hyperlink{ref-Gelman2008}{Gelman et al., 2008}).
See supplement XXXX for more detail.
The Stan code use to fit models is available from Github at: \url{https://github.com/mattocci27/leaf-disc}.
Convergence of the posterior distribution was assessed with the Gelman-Rubin statistic with a convergence threshold of 1.1 for all parameters (\protect\hyperlink{ref-Gelman2013}{Gelman et al., 2013}).

@@

where \(CV_1 = s/\bar{x}\), \(s\) is the sample standard deviation and \(\bar{x}\) is the sample mean, \emph{N} is the sample size, and \(\gamma_1\) and \(\gamma_2\) are the skewness and kurtosis of the trait distribution.
Bao's CV estimator is a robust method to quantify ITV based on coefficient of variation (CV) when sample size is small (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
We calulcated CV for species that have at least 5 indivdiuals as recommended in Westerband et al. (\protect\hyperlink{ref-Westerband2021}{2021}).
Ideally, 20 individuals for each species are required for robust estimation of CV {[}i.e., \textless5\% differences from the true ITV; Yang et al. (\protect\hyperlink{ref-Yang2020}{2020}){]}.

@@

@@

\textbf{Fig. 4.}
Relationships between coefficient of variation (Bao's CV estimator, Eq. 5) in leaf trait values determined by using whole leaves and leaf discs: (a) leaf mass per area (LMA).
The correlation is significant (\emph{P} \textless{} 0.001).
Details as in Fig. 1.

>>>>

The primary function of leaves is to return photosynthetic revenue on the investment that has been made in constructing the leaf (i.e., leaf economic spectrum, \protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Westoby2013}{Westoby et al., 2013}).
Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is a key trait in the leaf economic spectrum (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Poorter2009}{Poorter et al., 2009}; \protect\hyperlink{ref-Onoda2017}{Onoda et al., 2017}).
Generally, resource-acquisitive species (fast-growing species) tend to have low LMA values, showing high photosynthesis, high nutrients, and often have fast leaf turnover (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}).
In contrast, resource-conservative species (slow-growing species) often have higher LMA values with the opposite patterns (\protect\hyperlink{ref-Garnier1994}{Garnier and Laurent, 1994}; \protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Reich2014}{Reich, 2014}; \protect\hyperlink{ref-Diaz2016}{Díaz et al., 2016}).
The LMA is also frequently used in plant growth analysis (\protect\hyperlink{ref-Evans1972}{Evans, 1972}; \protect\hyperlink{ref-Poorter2014}{Poorter et al., 2014}; \protect\hyperlink{ref-Falster2018}{Falster et al., 2018}) because relative growth rates (RGR) can be decomposed into the product of net assimilation rate (NAR), leaf mass ratio (LMR) and LMA (i.e., RGR = NAR \(\times\) LMR \(\times\) LMA\textsuperscript{-1}).
Another appealing feature of LMA is that it is relatively easy to measure large numbers of species (i.e., `soft' trait, \protect\hyperlink{ref-Diaz2004}{Díaz et al., 2004}).
Therefore, LMA has been of interests to ecologists and widely used since the first report more than a century ago (\protect\hyperlink{ref-Hanson1917}{Hanson, 1917}).
Actually, LMA has one of the best species coverage in leaf traits of the TRY plant data database (16,460 species) and was also the most often requested leaf trait (2,977 out of 7,330 requests), followed by leaf by leaf nitrogen (N) contents per leaf dry mass (12,238 species, 1,938 requests, \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020} {[}TRY version 5, status October 1 2019{]})

@@

Since larger leaves tend to invest more of their mass into dense midribs and petiole for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006}, \protect\hyperlink{ref-Niinemets2007}{2007}; \protect\hyperlink{ref-Li2022}{Li, Shi, et al., 2022}; \protect\hyperlink{ref-Li2022a}{Li, Zheng, et al., 2022}), and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986})), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.
(\textbf{add leaf density})
If leaf disc LMA largely and consistently underestimates whole-leaf LMA (i.e., differences in means), some calibrations may be required to combine or compare those different estimates (\protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}).
If divergencies between the estimates based on the different methods are large and inconsistent (i.e., differences in variances and low \emph{R\textsuperscript{2}} values), this is difficult to calibrate and should inflate errors in the subsequent analyses.
To date, however, only a database from a single region, Panama Plant Traits Database (\protect\hyperlink{ref-Wright2010}{Wright et al., 2010}), is available in the TRY (\protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020}) that have both estimates of LMA from small leaf discs and whole leaves including petioles, limiting of our understanding of under what conditions estimates of LMA from leaf discs are reliable estimates of whole-leaf LMA.

@@

A bivariate trait relationship between disc-based and whole-leaf log-transformed LMA was summarized with variance explained (\emph{R\textsuperscript{2}}) based on Pearson correlations and with a standardized major axis (SMA) regression (\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the species.

A SMA analysis was run using the R package \emph{smatr} (\protect\hyperlink{ref-Warton2012a}{Warton et al., 2012}); this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
Confidence intervals of SMA estimates were based on 2000 bootstraps.

@@

where \(\tilde{\sigma_i}\) is a hyperparameter for \(\sigma_i\) ,
\(\omega^2\) is a scaling hyperparameter, and \(\gamma\) are coefficients.
To allow comparisons among parameter estimates, \(\mathrm{ln}(LD)\), \(\mathrm{ln}(LA)\), and \(\mathrm{ln}(LT)\) were scaled to a mean of 0 and standard deviation of 1.
Note that this model does not include measurement errors of leaf disc LMA implemented in the previous SMA analysis, because there are too many scaling parameters

Posterior distributions of all parameters were estimated using the Hamiltonian Monte Carlo algorithm (HMC) implemented in Stan (\protect\hyperlink{ref-Carpenter2017}{Carpenter et al., 2017}) using the weakly-informative priors (\protect\hyperlink{ref-Gelman2008}{Gelman et al., 2008}).
See Appendix SX for more detail.
The Stan code use to fit models is available from Github at: \url{https://github.com/mattocci27/leaf-disc}.
Convergence of the posterior distribution was assessed with the Gelman-Rubin statistic with a convergence threshold of 1.1 for all parameters (\protect\hyperlink{ref-Gelman2013}{Gelman et al., 2013}).

@@

where \(CV_1 = s/\bar{x}\), \(s\) is the sample standard deviation and \(\bar{x}\) is the sample mean, \emph{N} is the sample size, and \(\gamma_1\) and \(\gamma_2\) are the skewness and kurtosis of the trait distribution.
Bao's CV estimator is a robust method to quantify ITV based on a coefficient of variation (CV) when sample size is small (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
We calulcated CV for species that have at least 5 indivdiuals as recommended in Westerband et al. (\protect\hyperlink{ref-Westerband2021}{2021}).
Ideally, 20 individuals for each species are required for robust estimation of CV {[}i.e., \textless5\% differences from the true ITV; Yang et al. (\protect\hyperlink{ref-Yang2020}{2020}){]}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Li2022}{}}%
Li, Y., P. Shi, Ü. Niinemets, Y. Song, K. Yu, J. Schrader, and K. J. Niklas. 2022. \href{https://doi.org/10.1002/ajb2.1812}{Diminishing returns among lamina fresh and dry mass, surface area, and petiole fresh mass among nine {Lauraceae} species}. \emph{American Journal of Botany} 109: 377--392.

\leavevmode\vadjust pre{\hypertarget{ref-Li2022a}{}}%
Li, Y., Y. Zheng, D. A. Ratkowsky, H. Wei, and P. Shi. 2022. \href{https://doi.org/10.3389/fpls.2021.822907}{Application of an {Ovate Leaf Shape Model} to {Evaluate Leaf Bilateral Asymmetry} and {Calculate Lamina Centroid Location}}. \emph{Frontiers in Plant Science} 12: 822907.

@@

\textbf{Fig. 4.}
Relationships between coefficient of variation (Bao's CV estimator, Eq. 5) in LMA values determined by using whole leaves and leaf discs.
The correlation is significant (\emph{P} \textless{} 0.001).
Details as in Fig. 1.
